---
title: "MA615 Probset2"
author: "Lintong Li"
date: "2022-09-26"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Q1
```{r}
library(ggplot2)
setwd("C:/Users/Cici/Desktop/22fallhw/615hw/proset2")
veh1 <- read.csv(file="vehicles.CSV",header=T,sep=",")
veh1$phevBlended <- as.logical(veh1$phevBlended)
veh1sub <-subset(veh1,select=c("fuelCost08","year","make","city08","highway08","mpgData","phevBlended"))
veh1sub <- subset(veh1sub, phevBlended == FALSE)
ggplot(data = veh1sub, aes(x = year, y =fuelCost08))+
geom_point(color = "grey", size = 3)+
geom_smooth(method = 'gam',color="red")+
labs(x = "40 year span 1984 through 2023",
y = "Annual fuel cost",
title = "Fuel economy over the 40 years span 1984 through 2023"
)
```
Summary: The plot shows that the change in fuel economy over the 40 years span 1984 through 2023.


```{r}
veh2 <- subset(veh1,make == c("Dodge","Jeep","Toyota"))
ggplot(data = veh2, aes(x=year, y=city08, group=make, color=make)) +
geom_line(size = 2)+
labs(
x = "40 year span 1984 through 2023",
y = "MPG City",
title = "MPG City over 40 years span 1984 through 2023"
)
```
Summary: The plot shows that the change in MPG City over the 40 years span 1984 through 2023

```{r}
ggplot(data = veh2, aes(x=year, y=highway08, group=make, color=make)) +
geom_line(size = 2)+
labs(
x = "40 year span 1984 through 2023",
y = "MPG Highway",
title = "MPG Highway over 40 years span 1984 through 2023"
)
```
Summary: The plot shows that the change in MPG Highway over the 40 years span 1984 through 2023

From 3 selection, Toyota have made the most progress.

Q2
```{r}
library(tidyverse)
```

```{r}
setwd("C:/Users/Cici/Desktop/22fallhw/615hw/proset2")
IXI <- read.csv(file="IXIC21-22.CSV",header=T,sep=",")

```

```{r}
library(tidyquant)
```

```{r}
IXI <- read_csv("IXIC21-22.csv")

IXI %>%
  ggplot(aes(x=Date,y=Close)) + geom_candlestick(aes(open=Open,high=High,low=Low,close=Close)) + labs(title='Candlestick Chart',y='Close',x='Date') + 
  scale_x_date(date_labels = '%m-%Y')
```
Summary: The candlestick plot shows that the change in closing price from Sep.20, 2021 to Sep.20,2022 with overall download trend.
Q3

3.1
```{r}
setwd("C:/Users/Cici/Desktop/22fallhw/615hw/proset2")
rural <- read.csv(file="ruralCapacityData.CSV",header=T,sep=",")
```

```{r}
ruralsub <- subset(rural, County != "Bernalillo County")
ruralsub
```

```{r}
ggplot(data=ruralsub,aes(x=per_fam_below_pov, y=cap_index))+
  geom_point(color="red",size=3)+
  geom_smooth(method = 'loess', formula='y ~ x',span=0.5)+
  labs(title="RCI vs per_fam_below_pov",x="Percentage of families below the poverty level",y="Rural capacity index")
```
Summary: The plot shows the relationship between Percentage of families below the poverty level and Rural capacity index.

3.2
```{r}
ggplot(data=ruralsub,aes(x=per_over_25_with_bach,y=house_broadband,color=cap_index))+
  geom_point(size=3)+
  labs(title="house_broadband vs per_over_25_with_bach",x="Percent of population 25 and over with a bachelors degree",y="Total households with broadband connection")
```
Summary: The plot shows the relationship between Percent of population 25 and over with a bachelors degree and Total households with broadband connection with different level of Rural capacity index.

3.3
```{r}
ruralsub_1 <- subset(ruralsub, pop_total < 16000)
ggplot(data=ruralsub_1,aes(x=pop_total, y=cap_index))+
  geom_point(color="red",size=3)+
  geom_smooth(method = 'loess', formula='y ~ x',span=0.5)+
  labs(title="RCI vs Total population < 16000 ",x="Total population < 16000",y="Rural capacity index")
```
Summary: The plot shows that the relationship between Total population < 16000 and RCI.

```{r}
ruralsub_2 <- subset(ruralsub, pop_total < 55000 & pop_total > 16000)
ggplot(data=ruralsub_2,aes(x=pop_total, y=cap_index))+
  geom_point(color="red",size=3)+
  geom_smooth(method = 'loess', formula='y ~ x',span=0.5)+
  labs(title="RCI vs Total population between 16000 and 55000",x="pop_total < 55000 & pop_total > 16000",y="Rural capacity index")

```
Summary: The plot shows that the relationship between Total pop_total < 55000 & pop_total > 16000 and RCI.


```{r}
ruralsub_3 <- subset(ruralsub, pop_total > 55000)
ggplot(data=ruralsub_3,aes(x=pop_total, y=cap_index))+
  geom_point(color="red",size=3)+
  geom_smooth(method = 'loess', formula='y ~ x',span=0.5)+
  labs(title="RCI vs Total population >55000",x="pop_total > 55000",y="Rural capacity index")
```
Summary: The plot shows the relationship between Total population >55000 and RCI.


